---
output:
  pdf_document: default
  html_document: default
---

# Appendix 1: code for creating visualisations

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, message = FALSE, warnings = FALSE, fig.width = 12, fig.height = 7)
```

```{r}
library(tidyverse)
theme_set(theme_bw())
df <- read_csv("segments_old.csv", na = "")
df$label <- paste(df$Sign, df$segment)
colnames(df)
```

```{r}
data_frame(value = colMeans(!is.na(df[,-c(1, 12, 21:26, 33)])),
           features = names(colMeans(!is.na(df[,-c(1, 12, 21:26, 33)])))) %>% 
  mutate(features = reorder(features, value)) %>% 
  ggplot(aes(features, value, label = round(value, 3)))+
  ggrepel::geom_text_repel()+
  geom_point()+
  coord_flip()+
  labs(x="", y = "ratio in the whole dataset")
```

```{r}
read_csv("segments_old.csv", na = "") %>% 
  select(-c(1,12, 21:26))  ->
  df_mca

df_mca <- as.data.frame(sapply(df_mca , factor))

MCA <- MASS::mca(df_mca)
df <- cbind(df, MCA$rs)
variables <- as_data_frame(MCA$cs)
variables$var_names <- rownames(MCA$cs)
```

##  {.tabset .tabset-fade .tabset-pills}

### Meaning
```{r}
df %>% 
  ggplot(aes(`1`, `2`, label = label))+
  geom_text()
```

### H1.FingerSelection
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 FingerSelection`))+
  geom_point()+
  stat_ellipse()
```

### H1.Aperture
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 Aperture`))+
  geom_point()+
  stat_ellipse()
```

### H1.Curve
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 Curve`))+
  geom_point()+
  stat_ellipse()
```

### H1.Bent
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 Bent`))+
  geom_point()+
  stat_ellipse()
```

### H1.Facing
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 Facing`))+
  geom_point()+
  stat_ellipse()
```

### H1.Focus
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 Focus`))+
  geom_point()+
  stat_ellipse()
```

### H1.Width
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H1 Width`))+
  geom_point()+
  stat_ellipse()
```

### Dynamic.Orientation
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `Dynamic Orientation`))+
  geom_point()+
  stat_ellipse()
```

### Location
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = Location))+
  geom_point()+
  stat_ellipse()
```

### Plane
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = Plane))+
  geom_point()+
  stat_ellipse()
```

### Settings
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = Settings))+
  geom_point()+
  stat_ellipse()
```

### Path
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = Path))+
  geom_point()+
  stat_ellipse()
```

### H2.FingerSelection
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 FingerSelection`))+
  geom_point()+
  stat_ellipse()
```

### H2.Aperture
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 Aperture`))+
  geom_point()+
  stat_ellipse()
```

### H2.Curve
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 Curve`))+
  geom_point()+
  stat_ellipse()
```

### H2.Bent
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 Bent`))+
  geom_point()+
  stat_ellipse()
```

### H2.Width
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 Width`))+
  geom_point()+
  stat_ellipse()
```

### H2.Facing
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 Facing`))+
  geom_point()+
  stat_ellipse()
```

### H2.Focus
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = `H2 Focus`))+
  geom_point()+
  stat_ellipse()
```

### manner_tense
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_tense))+
  geom_point()+
  stat_ellipse()
```

### manner_repeated
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_repeated))+
  geom_point()+
  stat_ellipse()
```

### manner_laceration
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_laceration))+
  geom_point()+
  stat_ellipse()
```

### manner_symmetrical
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_symmetrical))+
  geom_point()+
  stat_ellipse()
```

### manner_alternating
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_alternating))+
  geom_point()+
  stat_ellipse()
```

### manner_biderectional
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_biderectional))+
  geom_point()+
  stat_ellipse()
```

### manner_alternating
```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = manner_alternating))+
  geom_point()+
  stat_ellipse()
```

### iconicity

```{r}
df %>% 
  ggplot(aes(`1`, `2`, color = iconic))+
  geom_point()+
  stat_ellipse()
```


```{r}
df %>% 
  arrange(desc(`1`)) %>% 
  select(labeled_url, `1`,`2`) %>% 
  DT::datatable(escape = FALSE, options = list(pageLength = 10, dom = 'ftip'))
```

```{r}
variables %>% 
  ggplot(aes(`1`, `2`, label = var_names))+
  geom_text()
#  scale_x_continuous(limits = c(-0.03, 0.06))
```

```{r}
df %>% 
  ggplot(aes(`1`, `2`))+
  geom_text(data = variables, aes(`1`, `2`, label = var_names))+
  geom_point(color = "red")
```